---
title: "Who are the elected representatives?"
output:
html_document: default
css: styles.css
---

```{r= setup, include=FALSE}
address1 <- "2199 S University Blvd, Denver, CO 80208"

address2 <- "Puyallup, WA"
```

# This is a list of all elected representatives for two US locations.

This is a report about the political representatives for residents of **`r address1`** and **`r address2`**. The data is extracted from [Google Civic Data API.](https://developers.google.com/civic-information/). The table includes the **Position, Name, Party, Email address, Phone, and Photo** of the representatives.

## Representatives for `r address1`

```{r setup, include=FALSE}

library(knitr)
library(httr)
library(jsonlite)
library(stringr)
library(dplyr)
source("~/Documents/keys.R")
source('process-data.R')
knitr::opts_chunk$set(echo=FALSE, message=FALSE)

```


```{r}
tbl <- repTable(address1)
knitr::kable(tbl)

```

## Representatives for `r address2`


```{r}
tbl <- repTable(address2)
knitr::kable(tbl)
```

